---
title: "Introduction to AutomaticCellTypeIdentification"
author: "Bingbing Xie"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
vignette: >
  %\VignetteIndexEntry{Introduction to AutomaticCellTypeIdentification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6, 
  fig.height = 4.8, 
  cache = TRUE
)
```

## Summary

This tutorial provide demo of three types robotic methods.

###Install from R
After installing all needed R packages, the conda environment of python-based methods ('ACTINN','CELLBALST','DigitalCellSorter','Markercount','MARS','scHPL','scVI') is needed to install.

###Install from docker
All need R and python packages are install in docker file.

Start from docker:
```docker
sudo docker run -it registry.cn-hangzhou.aliyuncs.com/xiebb123456/automaticcelltypeidentification
```

## Application of `AutomaticCellTypeIdentification`

First, we'll load the `AutomaticCellTypeIdentification` package and `Seurat`.

```{r load_libraries,  message=FALSE, results='hide', warning=FALSE}
library("AutomaticCellTypeIdentification")
library("Seurat")
```

In this tutorial, we'll use the scRNA-seq of Liver tissue in Tabular Muris as training (10X) and testing (SM2) dataset. The demo data could be download from testdata. 

```{r read_data}
load('testdata/Liver_GSE109774_10X.RData')
load('testdata/Liver_GSE109774_SM2.RData')
```

Then prepare the count matrix and canonical marker.

```{r process_data}
train = as.matrix(GetAssayData(train_object,slot='counts'))
test = as.matrix(GetAssayData(test_object,slot='counts'))
label_train = train_object$celltyperaw
markers = diffmarker(train,label_train,only.pos=T)
```

Firstly,let's use eagersupervised method to predict cell type of testing dataset by ```Seurat```.

```{r process_data}
predict_label = eagersupervised(train,test,label_train,method='seurat')
```

You can check the predict label or compare the true and predict label through following command:

```{r process_data}
table(predict_label)
table(test_object$celltyperaw,predict_label)
```

Secondly,let's use lazysupervised method to predict cell type of testing dataset by ```CELLBLAST```.

```{r process_data}
predict_label = lazysupervised(train,test,label_train,method='CELLBLAST')
```

lastly,let's use markersupervised method to predict cell type of testing dataset by ```SCSA```, markersupervised method need marker instead of expression matrix, here we use differential expressed marker from training dataset as input.

```{r process_data}
predict_label = markersupervised(test,markers$marker_5,method='SCSA')
```

Note: python-based methods should initiate first 

reticulate::use_condaenv('cellblast')
reticulate::py_config()
library(AutomaticCellTypeIdentification)
library("Seurat")
load('testdata/Liver_GSE109774_10X.RData')
load('testdata/Liver_GSE109774_SM2.RData')
train = as.matrix(GetAssayData(train_object,slot='counts'))
test = as.matrix(GetAssayData(test_object,slot='counts'))
label_train = train_object$celltyperaw
markers = diffmarker(train,label_train,only.pos=T)
predict_label = lazysupervised(train,test,label_train,method='CELLBLAST')

